Title

### 2024-01-02 Quarto Template.qmd
quarto template

```{r libraries}
#| include: false
library(tidyverse)
```

@@

```{r}
#| label: tbl-planets
#| tbl-cap: Planets

@@

```{r}
#| label: fig-planets
#| fig-cap: Planets

>>>>

```{r setup}
#| include: false
library(tidyverse)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r}
#| label: tbl-planets
#| tbl-cap: Planets
```

@@

```{r}
#| label: fig-planets
#| fig-cap: Planets
```
